{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}

### 2025-07-22 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

        Before we start, here are some techinical details regarding conditional expectations. 
        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some sigma algebra. 
        The conditional expectation exists, and it's unique. 

@@

        \begin{theorem}[SNAG descent lemma in expectations]\label{thm:snag-descent-expe}

        \end{theorem}
        \begin{proof}

        \end{proof}
\section{Discussion, interpolation helps but, it's not enough}
    \subsection{The no error case}
    \subsection{The degenerate case}

>>>>

@@

        \begin{theorem}[SNAG convergence rate]\label{thm:snag-convergence}
            Suppose that the sequence $(y_k, x_k, v_k)_{k \ge 0}$ is generated by algorithms satisfying Definition \ref{def:SNAG}. 
            Assuming that it's generated by the stochastic gradient operator as in Definition \ref{def:stoch-pg-opt-rel-err}. 
            For all $\bar x \in \RR^n$, for all $k \ge 1$, the convergence in expectation, can be compactly written as: 
                \expect \Phi_k &\le
                    \prod_{i = 1}^k \lambda_i
                \right)\expect_k \Phi_0 + 
                \sum_{j = 0}^{k}\left(
                    \prod_{i = k - j}^k \lambda_i
                \right)\expect R_{k - j - 1}
                + \expect R_k.
            Where: 
                \item $\Phi_k := F(x_k) - F(\bar x) + \alpha_k^2(L - \epsilon_k)/2 \Vert v_k - \bar x\Vert^2$, 
                \item $R_k := \frac{\epsilon_k}{2}\Vert y_k - x_k\Vert^2$, 
                \item $\lambda_k := (1 - \alpha_k)\max(1, L\rho_{k - 1}/(L - \epsilon_{k - 1}))$. 
            Denote $\expect_k$ to be the conditional expectation based on random variables $\tilde \nabla f(y_i)$ for $i = 1, \ldots, k - 1$. 
            The base case has $\expect_0$ which is the overall expectation. 
            Fix any $\bar x \in \RR^n$ throughout. 
            Consider any $k \ge 1$. 
            Under the new notations, the relations from Theorem \ref{thm:snag-descent} yields 
                & \expect_k \Phi_k 
                &= \expect_k F(x_k) - F(\bar x) + \frac{\alpha_k(L - \epsilon_k)}{2}\expect_k \Vert v_k - \bar x\Vert^2
                    F(x_{k - 1})- F(\bar x) + \frac{\alpha_{k - 1}^2 L \rho_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{\epsilon_k}{2}\expect_k \Vert y_k - x_k\Vert^2
                &= (1 - \alpha_k)\left(
                    F(x_{k - 1})- F(\bar x) + \frac{\alpha_{k - 1}^2 L \rho_{k - 1}}{2}
                        \frac{L - \epsilon_{k - 1}}{L}
                        \frac{L}{L - \epsilon_{k - 1}}
                    \Vert \bar x - v_{k - 1}\Vert^2
                + \expect_k R_k
                &= (1 - \alpha_k)\left(
                    F(x_{k - 1})- F(\bar x) 
                    + \frac{\alpha_{k - 1}^2(L - \epsilon_{k - 1})}{2}
                        \frac{L\rho_{k - 1}}{L - \epsilon_{k - 1}}
                    \Vert \bar x - v_{k - 1}\Vert^2
                + \expect_k R_k
                &= (1 - \alpha_k)\max\left(
                    1, \frac{L\rho_{k - 1}}{L - \epsilon_{k - 1}}
                \right)\left(
                    F(x_{k - 1})- F(\bar x) 
                    + \frac{\alpha_{k - 1}^2(L - \epsilon_{k - 1})}{2}
                    \Vert \bar x - v_{k - 1}\Vert^2
                + \expect_k R_k
                &= \lambda_k \Phi_{k - 1} + \expect_k R_k.
            At \circled{1}, we used Theorem \ref{thm:snag-descent}. 
            Taking the full expectation, which is $\expect_0$ on both sides of the inequality above it yields 
            \begin{align}\label{ineq:snag-descent-expe-pitem-1}
                \expect_0 \Phi_{k} \le \lambda_{k + 1}\expect_0 \Phi_k + \expect_0 R_{k + 1}. 
            Since this is true for all $k \ge 0$ in $\N$, we are now in position to verify the following inductive hypothesis 
            \begin{align}\tag{IH}
                \expect_0 \Phi_k &\le
                    \prod_{i = 1}^k \lambda_i
                \right)\expect_k \Phi_0 + 
                \sum_{j = 0}^{k}\left(
                    \prod_{i = k - j}^k \lambda_i
                \right)\expect_0 R_{k - j - 1}
                + \expect_0 R_k.
            Use Inequality \ref{ineq:snag-descent-expe-pitem-1} with $k$ as $k + 1$, the inductive proof follows: 
                \expect_0 \Phi_{k + 1} &\le 
                \lambda_{k + 1}\expect_0\Phi_k 
                + \expect_0 R_{k + 1}
                &\hspace{-0.2em}\underset{\text{(IH)}}{\le} \lambda_{k + 1}\left(
                        \prod_{i = 1}^k \lambda_i
                    \right)\expect_k \Phi_0 
                    + \sum_{j = 0}^{k}\left(
                        \prod_{i = k - j}^k \lambda_i
                    \right)\expect_0 R_{k - j - 1}
                    + \expect_0 R_k
                + \expect_0 R_{k + 1}
                    \prod_{i = 1}^{k + 1} \lambda_i
                \right)\expect_k \Phi_0
                + \sum_{j = 0}^{k}\left(
                    \prod_{i = k - j}^{k + 1}\lambda_i
                \right)\expect_0 R_{k - j - 1}
                + \lambda_{k + 1}\expect_0 R_k 
                + \expect_0 R_{k + 1}
                    \prod_{i = 1}^{k + 1} \lambda_i
                \right)\expect_k \Phi_0
                + \sum_{j = 1}^{k + 1}\left(
                    \prod_{i = k- j}^{k + 1}\lambda_i
                \right)\expect_0 R_{k + 1 - j}
                + \sum_{j = 0}^0 \prod_{i = k + 1 - j}^{k + 1}\lambda_{k + 1}\expect_0 R_k 
                + \expect_0 R_{k + 1}
                    \prod_{i = 1}^{k + 1} \lambda_i
                \right)\expect_k \Phi_0
                + \sum_{j = 0}^{k + 1}\left(
                    \prod_{i = k- j}^{k + 1}\lambda_i
                \right)\expect_0 R_{k + 1 - j}
                + \expect_0 R_{k + 1}. 
            Therefore, the inductive hypothesis holds. 
    \subsection{Discussion of he error schedules}
        Let's talk about Theorem \ref{thm:snag-convergence} here. 
        With the compact representations, we can make see what is happening here. 
        The inequality of the convergence consists of several quantities: 
            \item $\Phi_0$, the base case and a bounded quantities, depends on initial iterate $v_{-1}, x_{-1}$. 
            \item $\lambda_k$, a sequence controling the convergence, involving relaxation parameters $\rho_{k - 1}$ and, the error $\epsilon_k$. 
            \item $R_k$, an error term that, it's none trivial to group with the other terms of the inequality. 
        Under some assumptions, and conditions, we can have some type of convergence rate. 
\section{Interpolation helps but, it's very unclear if it's sufficient}
    \subsection{The no error case}
    \subsection{The degenerate case}
